Variant detection model with improved robustness and accuracy for low-depth targeted next-generation sequencing data

### 2013-12-30 doc/ISMB2014/RVD3.tex
Paper draft ISMB2014.

Two 400bp DNA sequences that are identical except at 14 loci with variant bases were synthesized and clonally isolated and labeled case and control. Sample of the case and control DNA were mixed at defined fractions to yield defined minor allele frequencies (MAFs) of 0.1\%, 0.3\%, 1\%, 10\%, and 100\%. More details of the experimental protocol are available from the original publication~\citep{Flaherty:2011ja}. We aligned the reads to the reference sequence using BWA v0.7.4 with the -C50 option to filter for high mapping quality reads.

To simulate lower coverage data while retaining the error structure of real NGS data, BAM files for the synthetic DNA data were downsampled $10\times$, $100\times$, $1,000\times$, and $10,000\times$ using Picard v1.96. The final data set contains read pairs for three replicates of each case and pairs of reads three replicates for the control sample giving $N=6$ replicates for the control and each MAF level.

\subsection{Yeast Data}

@@

\subsection{Model Structure}\label{sec:model_structure}
RVD3 is based on a hierarchical Bayesian model. Through hypothesis test on case and control samples by RVD3, we can call the variants sucsessfully. Now the definitions for sample data are given: $r_{ji}$ is the number of reads with a non-reference base at position $j$ in replicate $i$, and $n_{ji}$ is the total number of reads at position $j$ in replicate $i$. Three parameters of the model are: $\mu_0$, a global error rate; $M_0$, the global position which estimates the variation in the error rate across the positioins; priors for $M_j$, two kinds of priors are log-normal prior and Jeffreys prior, which enhanced the former RVD model [XXX]. Here $M_j$ is the local precision measures the alteration in the error rate across replicates at position $j$. The graphical chart for RVD3 are shown in Figure~\ref{fig:graphical_model}.
RVD3 hierarchically includes four levels of samplings: $r_{ji} | n_{ji} \thicksim \text{Binomial}(\theta_{ji}, n_{ji})$ models the variation due to sampling the pool of DNA molecules on the sequencer. $\theta_{ji} \thicksim \text{Beta}(\mu_j, M_j)$ models the variation caused by experimental repeatability. The variation in error rate due to sequence context is modeled by $\mu_j \thicksim \text{Beta}(\mu_0, M_0)$. And the local precision is modeled by $ M_{j} \thicksim \text{log-normal}(\mu, \sigma)$ (log-normal prior), and $\pi\left({M}_{j}\right)$ (Jeffreys prior).

\begin{figure}[h]
\begin{center}
\includegraphics[width=120mm]{figs/RVD3_model.pdf}
\caption{RVD3 Graphical Model}
\label{fig:graphical_model}
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%
% Inference & Hypothesis Testing
%%%%%%%%%%%%%%%%%%
\subsection{Inference and Hypothesis Testing}
Metropolis-within-Gibbs sampling is evolved for inference. Algorithm 1 shows the inference process and the detail are illustrated.

\begin{algorithm}[ht]
\caption{Metropolis-within-Gibbs Algorithm}
\label{alg:metro_gibbs}
\begin{algorithmic}[1]

\State Initialize $\theta$, $\mu$, $M$, $\mu_0$, $M_0$
\Repeat
\For {each location j}
  \State Draw T samples from $p \left( \mu_j |\theta_{ij},\mu_0,M_0\right)$ using M--H \Comment{Sample $\mu_j$}
  \State Set $\mu_j$ to the sample median for the T samples
  \State Draw T samples from $p \left( M_{j} |\mu,\sigma, \theta_{ji},\mu_j\right)$ using M--H \Comment{Sample $M_j$}

@@

@@

We resample from the proposal if the sample is outside of the support of the posterior distribution. We typically discard 20\% of the sample for burn-in and thin the chain by a factor of 2 to reduce autocorrelation among samples. Since, each position $j$ is exchangeable given the global hyperparameters $\mu_0$ and $M_0$ this sampling step can be distributed across up to $J$ processors.

%%%%%%%%%%%%%%%%%%
% Sampling Mj
%%%%%%%%%%%%%%%%%%
\subsubsection{Sampling from $p \left( M_{j} |\mu,\sigma, \theta_{ji},\mu_j\right)$}
For Jeffreys prior,since ${\theta }_{ji}\sim Beta\left( {\mu }_{j},{M}_{j}\right)$, the Fisher information is given by

@@

Now to calculate the equations to acquire the Fisher information, we assume there is only one replicate,

@@

\begin{equation}
\pi\left({M}_{j}\right) = [-\left(\Psi_{1}(M_{j}) - \Psi_{1}(\mu_{j} M_{j})\mu_{j}^{2} - \Psi_{1}((1-\mu_{j})M_{j}){(1-\mu_{j})^{2}}\right)]^{\frac{1}{2}}
\end{equation}

We have $ \theta_{ji}\thicksim\text{Beta}(\mu_{j},M_{j})$, and $ M_{j} \thicksim \text{log-normal}(\mu, \sigma)$. Since we cannot give an analytical form for this, so we sample from the posterior distribution using the Metropolis-Hastings algorithm.

%%%%%%%%%%%%%%%%%%
% Posterior Density Test
%%%%%%%%%%%%%%%%%%
\subsubsection{Posterior Density Test}\label{sec:hypothesis_test}
Metropolis-within-Gibbs provides samples from the posterior distribution of $\mu_j$ given the case or control data. For notational simplicity, we define the random variables associated with these two distributions $\tilde{\mu}_j^{\text{case}}$ and $\tilde{\mu}_j^{\text{control}}$.

A variant is called if $\tilde{\mu}_j^{\text{case}} > \tilde{\mu}_j^{\text{control}}$ with high confidence,
\begin{equation}\label{eqn:bayes_test}
	\Pr( \tilde{\mu}_j^{\text{case}} - \tilde{\mu}_j^{\text{control}} \geq \tau ) > 1-\alpha,
\end{equation}
where $\tau$ is a detection threshold and $1-\alpha$ is a confidence level. We draw a sample from the posterior distribution $\tilde{\mu}_j^{\Delta} \triangleq \tilde{\mu}_j^{\text{case}} - \tilde{\mu}_j^{\text{control}}$ by simple random sampling with replacement from $\tilde{\mu}_j^{\text{case}}$ and $\tilde{\mu}_j^{\text{control}}$. We set $\tau = 0$ in our experiment.

%%%%%%%%%%%%%%%%%%%%%%%%
% Priors for precision parameter
%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Priors for precision parameter}
\subsubsection{Improper Prior}
Playing no prior on M is an implicit improper prior. So we coniderated about two typical priors: noninformation prior - Jeffreys prior, and information prior - log-normal prior.

\subsubsection{Jeffreys Prior}
Jeffreys prior is proposed for invariance by Harold Jeffreys (1946), and defined in terms of the Fisher information. For our ploblem,
\begin{equation}\label{eqn:JefferyPrior}
\pi\left({M}_{j}\right)= I\left({M}_{j}\right)^{\frac{1}{2}}
\end{equation}

\subsubsection{Log-normal Prior}
In log-normal distribution, the parameters denoted $\mu$ and $\sigma$, the mean and standard deviation respectively. Log-normal prior was used on $ M_{j}$.
Incorporate log-normal prior on $M_{j}$.

%%%%%%%%%%%%%%%%%%
% Sensitivity analysis of priors
%%%%%%%%%%%%%%%%%%
\subsection{Sensitivity analysis of priors}
In order to examine the robustness of RVD3 to changes of different priors, we performed information prior (Log-normal) and noninformation prior (Jeffreys). We found that RVD3 is robust to changing the priors. The RVD3 algorithm provides estimates of model parameters and latent variables given the data.

We show several of these parameters in Figure~\ref{fig:M_jeffrey} and Figure ~\ref{fig:M_lognormal}. The left column of these two figures show the read depth for each of the six bam files (three replicates each with two read pairs) for each data set. Because the DNA was not sheared and ligated prior to sequencing, the read depth drops to zero at the boundaries. For the 100\% mutant data set, the read depth drops at the mutant locations. This is due to the parameters imposed at the alignment stage.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=120mm]{figs/M_lognormal.pdf}
\caption{Key parameters for RVD3 model with log-normal prior for synthetic DNA data sets.}
\label{fig:M_lognormal}
\end{center}
\end{figure}

The right column of Figure~\ref{fig:M_jeffrey} and Figure~\ref{fig:M_lognormal} show the parameter estimates $\hat{M}_j$ and $\hat{M}_0$ for each data set. $M_j$ measures the variance between replicates at location $j$. There is little variability across positions indicating that the replication variance does not change greatly across position. Furthermore, $M_j$ from Jeffreys prior [Figure~\ref{fig:M_jeffrey}] the M value drops at the mutant positions when the data is 10\% and 100\% mutant, which is not shown in log-normal prior [Figure~\ref{fig:M_lognormal}]. Additionally, the error rate across positions is captured by the $M_0$ parameter shown as a horizontal dotted line in the plots in the right column. $M_j$ is greater than $M_0$ the precision between replicates is higher than the precision across positions.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=170mm]{figs/prior_post_dilu_1.pdf}
\caption{Distribution of priors and posteriors when dilution is 1\%}
\label{fig:dilu_1}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=170mm]{figs/prior_post_dilu_10.pdf}
\caption{Distribution of priors and posteriors when dilution is 10\%}
\label{fig:dilu_10}
\end{center}
\end{figure}

Statistically, We analyzed the posteriors and priors for Jeffreys prior and log-normal prior. Figure~\ref{fig:dilu_1} and Figure~\ref{fig:dilu_10} show the distribution over different M values focused on 4 different locations (position 100 and 300 are mutant, and position 104 and 244 are non-mutant). The positions are chosen in the middle of the dase length. From the posterior distributions, non-mutant positions display normal and stable without a peak nor a strange shape. The Jeffreys' prior shows more information than the lognormal prior (flat) from the posterior curve. From the prior distribution, it shows our model wants to search for a small value for M.

To evaluate the performance of RVD3 model with priors, we generated receiver-operating characteristic curves (ROCs) for median read depth and minor allele frequencies (MAFs). Here the Bayesian test is used without the $\chi^2$ test. Figure~\ref{fig:ROC_jeffrey} and Figure~\ref{fig:ROC_lognormal} shows ROC curves with a fixed $\alpha=0.05$. The performance improves when the read depth goes up. (ROC shows that the model with priors performs better than improper prior situation especially on the small read depth). Noticed at the lowest depth (22) with 10.0\% mutant mixture, the sensitivity and specificity value are 1 and much better than the model without priors for $M_J$, which definitely demonstrates the advantage of priors.

\begin{figure}[h]
\begin{center}
\includegraphics[width=160mm]{tables/Sen_Speci.pdf}
\caption{Sensitivity/Specificity comparison of RVD3 with different priors.}
\label{tbl:SS}
\end{center}
\end{figure}

\begin{figure}[h]
\begin{center}
\includegraphics[width=160mm]{tables/FDR.pdf}
\caption{False Discovery Rate comparison of RVD3 with different priors.}
\label{tbl:FDR}
\end{center}
\end{figure}

Figure~\ref{tbl:SS} shows that the sensitivity and specificity of the RVD3 of different priors compared with the model without priors. Log-normal prior shows a higher sensitivity and specificity value than the Jeffreys prior.
Figure~\ref{tbl:FDR} shows the false discovery rate of the RVD3 with different priors. Jeffreys prior shows a smaller false discovery rate and higher accuracy than others. It is obvious no matter which pirors, the variant detection performance acquires lower FDR than the model without priors. Based on the various advantages for Jeffreys and log-normal prior, RVD3 can afford a more appropariate choice for the precision prior. Here we chose Jeffreys prior because it needs more attention to false discovery rate and accuracy for variants calling research, compared with the clinical experiment or diagnosis which cares more on true positive rate and true negative rate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Results of Jeffreys prior on yeast data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results of Jeffreys prior on yeast data}

We demonstrated our RVD3 model with Jeffreys piror on yeast data to identify the variants.

%%%%%%%%%%%%%%%%%%%
% Appendix B: Comparison Statistics
%%%%%%%%%%%%%%%%%%%

>>>>

Two 400bp DNA sequences differ only 14 single nucleotide positions. Sample of the case and control DNA were mixed to yield 0.1\%, 0.3\%, 1\%, 10\%, and 100\% defined minor allele frequencies (MAFs). The details of the experimental protocol are available from the original publication~\citep{Flaherty:2011ja}. We used BWA v0.7.5a to align the reads to the reference sequence with the -C50 option to remove the reads of high mapping quality. BAM files were sampled by $10\times$, $100\times$, $1,000\times$, and $10,000\times$ using Picard v1.104. The final data set contains read pairs for $N=6$ replicates for the control at different MAF levels.

\subsection{Yeast Data}
We first mapped the GSY1135 to Chromosome 10 in S288c reference genome by BWA v0.7.5a [XXX]. Then called SNPs by GATK UnifiedGenotyper and created a FASTA GSY1135 reference using GATK FastaAlternative [XXX].
Secondly, we downloaded generation 7 as control and generation 133 as case in experiment 1 from [XXX], and removed WT population using FASTX Barcode Splitter [XXX] and trimed the Nextera tag by Cutadapt v1.3.
Finally, the FASTQ files of case and control were mapped to GSY1135 reference and pileup files were generated using Samtools v0.1.19.

@@

\subsection{Model Structure}\label{sec:model_structure}
RVD3 is based on a hierarchical Bayesian model. Through hypothesis test on case and control samples by RVD3, we can call the variants sucsessfully. Now the definitions for sample data are given: $r_{ji}$ is the number of reads with a non-reference base at position $j$ in replicate $i$, and $n_{ji}$ is the total number of reads at position $j$ in replicate $i$. Three parameters of the model are: $\mu_0$, a global error rate; $M_0$, the global position which estimates the variation in the error rate across the positions; priors for $M_j$, two kinds of priors are log-normal prior and Jeffreys prior, which enhanced the former RVD model [XXX]. Here $M_j$ is the local precision measures the alteration in the error rate across replicates at position $j$. The graphical chart for RVD3 are shown in Figure~\ref{fig:graphical_model}.
RVD3 hierarchically includes four levels of samplings: $r_{ji} | n_{ji} \thicksim \text{Binomial}(\theta_{ji}, n_{ji})$ models the variation due to sampling the pool of DNA molecules on the sequencer. $\theta_{ji} \thicksim \text{Beta}(\mu_j, M_j)$ models the variation caused by experimental repeatability. The variation in error rate due to sequence context is modeled by $\mu_j \thicksim \text{Beta}(\mu_0, M_0)$. And the local precision is modeled by $ M_{j} \thicksim \text{log-normal}(\mu, \sigma)$ (log-normal prior), and $\pi\left({M}_{j}\right)$ (Jeffreys prior).

\begin{figure}[h]
\begin{center}
\includegraphics[width=100mm]{figs/RVD3_model.pdf}
\caption{RVD3 Graphical Model}
\label{fig:graphical_model}
\end{center}
\end{figure}

%%%%%%%%%%%%%%%%%%
% Inference & Hypothesis Testing
%%%%%%%%%%%%%%%%%%
\subsection{Inference and Hypothesis Testing}

\begin{algorithm}[ht]
\caption{Inference process for Metropolis-within-Gibbs}
\label{alg:metro_gibbs}
\begin{algorithmic}[1]

\State Initialize $\theta$, $\mu$, $M_j$, $\mu_0$, $M_0$
\Repeat
\For {each location j}
  \State Draw T samples from $p \left( \mu_j |\theta_{ij},\mu_0,M_0\right)$ using M--H \Comment{Sample $\mu_j$}
  \State Set $\mu_j$ to the sample median for the T samples
  \State Draw T samples from $p \left( M_{j} |\mu,\sigma, \theta_{ji},\mu_j\right)$ using M--H \Comment{Sample $M_j$}

@@

Metropolis-within-Gibbs sampling is evolved for inference. Algorithm 1 shows the inference process and the detail are also illustrated.

@@

We resampled from the proposal if the sample is outside of the support of the posterior distribution. We typically discard 20\% of the sample for burn-in and thin the chain by a factor of 2 to reduce autocorrelation among samples. Since, each position $j$ is exchangeable given the global hyperparameters $\mu_0$ and $M_0$ this sampling step can be distributed across up to $J$ processors.

%%%%%%%%%%%%%%%%%%
% Sampling Mj
%%%%%%%%%%%%%%%%%%
\subsubsection{Sampling from $p \left( M_{j} |\mu,\sigma, \theta_{ji},\mu_j\right)$}
For Jeffreys prior is from the Fisher information and ${\theta }_{ji}\sim Beta\left( {\mu }_{j},{M}_{j}\right)$,

@@

We calculated the equations (Appendix B) and obtained the Jeffreys' prior for $M_j$:

% \pi\left({M}_{j}\right) =
\begin{equation}
[-\left(\Psi_{1}(M_{j}) - \Psi_{1}(\mu_{j} M_{j})\mu_{j}^{2} - \Psi_{1}((1-\mu_{j})M_{j}){(1-\mu_{j})^{2}}\right)]^{\frac{1}{2}}
\end{equation}

We have $ \theta_{ji}\thicksim\text{Beta}(\mu_{j},M_{j})$, and $ M_{j} \thicksim \text{log-normal}(\mu, \sigma)$. Since we cannot provide an intepretive form for it, so Metropolis-Hastings algorithm was used to sample from the posterior distribution.

%%%%%%%%%%%%%%%%%%
% Posterior Density Test
%%%%%%%%%%%%%%%%%%
\subsubsection{Posterior Density Test}\label{sec:hypothesis_test}
Posterior distributions of $\mu_j$ for the control and case are achieved-  $\tilde{\mu}_j^{\text{case}}$ and $\tilde{\mu}_j^{\text{control}}$, by Metropolis-within-Gibbs. So we called a variant when $\tilde{\mu}_j^{\text{case}} > \tilde{\mu}_j^{\text{control}}$ with $1-\alpha$ confidence,
\begin{equation}\label{eqn:bayes_test}
	\Pr( \tilde{\mu}_j^{\text{case}} - \tilde{\mu}_j^{\text{control}} \geq \tau ) > 1-\alpha,
\end{equation}
where $\tau$ is a detection threshold and $1-\alpha$ is the confidence level. We set $\tau = 0$ in our experiment [XXX].

%%%%%%%%%%%%%%%%%%%%%%%%
% Priors for precision parameter
%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Priors for precision parameter}
%\subsubsection{Improper Prior}
Playing no prior on $ M_{j}$ is an implicit improper prior. An improper prior integrates to infinity, and may cause an improper posterior which results in an invalid inferences [XXX]. Because an improper prior is a bad choice since a step has to be taken to confirm the posterior is proper. We considered about two typical priors: non-information prior - Jeffreys prior, and information prior - log-normal prior.

%\subsubsection{Jeffreys Prior}
Jeffreys prior is proposed to establish a least informative prior that is automatically invariant to transformations by Harold Jeffreys (1946). It is defined in terms of the Fisher information and works well with a single parameter. In our research Jeffreys prior for $M_j$ is the square root of Fisher information of $M_j$. Log-normal prior is a typical prior for the beta density's parameters, $\theta_{ji} \thicksim \text{Beta}(\mu_j, M_j)$. So log-normal prior was incorporated in the model. The parameters of it denoted $\mu$ (mean) and $\sigma$ (standard deviation) respectively.

%%%%%%%%%%%%%%%%%%
% Sensitivity analysis of priors
%%%%%%%%%%%%%%%%%%
\subsection{Sensitivity analysis of priors}
In order to examine the robustness of RVD3 to changes of different priors, we performed information prior (log-normal) and non-information prior (Jeffreys). We found that RVD3 is robust to changing the priors. The RVD3 algorithm provides estimates of model parameters and latent variables given the data.

We show several of these parameters of the model with Jeffreys prior in Figure~\ref{fig:M_jeffrey}. The left column of is shows the read depth for each of the six BAM files (three replicates each with two read pairs) for each data set. Because the DNA was not sheared and ligated prior to sequencing, the read depth drops to zero at the boundaries. For the 100\% mutant data set, the read depth drops at the mutant locations. This is due to the parameters imposed at the alignment stage. The right column of Figure~\ref{fig:M_jeffrey} reveals the parameter estimates $\hat{M}_j$ and $\hat{M}_0$ for each data set. $M_j$ measures the variance between replicates at location $j$. There is little variability across positions indicating that the replication variance does not change greatly across position. Furthermore, $M_j$ from Jeffreys prior [Figure~\ref{fig:M_jeffrey}] across the M value drops at the mutant positions when the data is 10\% and 100\% mutant, which is not shown in log-normal prior [Figure~\ref{fig:M_lognormal}] in Appendix C. Additionally, the error rate across positions is captured by the $M_0$ parameter shown as a horizontal dotted line in the plots in the right column. $M_j$ is greater than $M_0$ the precision between replicates is higher than the precision across positions.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=170mm]{figs/post_prior_dilu_10.pdf}
\caption{Distribution of priors and posteriors when dilution is 10\%}
\label{fig:dilu_10}
\end{center}
\end{figure}

Statistically, We analyzed the posteriors and priors for Jeffreys prior and log-normal prior. Figure~\ref{fig:dilu_10} shows the probability distribution over different M values when dilution is 10\% at $100\times$ read depth rate. The positions are chosen in the middle of the base length- position 100 and 300 are mutant, and position 104 and 244 are non-mutant. From the posterior probability distributions are estimated by Gaussian Kernel Density [XXX]. From the figure non-mutant positions display normal and stable without a peak nor a strange shape. The Jeffreys' prior shows more information than the lognormal prior (flat) from the posterior curve. From the prior distribution, it shows our model wants to search for a small value for M.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=160mm]{tables/Sen_Speci.pdf}
\caption{Sensitivity/Specificity comparison of RVD3 with different priors.}
\label{tbl:SS}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=160mm]{tables/FDR.pdf}
\caption{False Discovery Rate comparison of RVD3 with different priors.}
\label{tbl:FDR}
\end{center}
\end{figure}

To evaluate the performance of RVD3 model with priors, we generated receiver-operating characteristic curves (ROCs) for median read depth and minor allele frequencies (MAFs). Here the Bayesian test is used without the $\chi^2$ test. Figure~\ref{fig:ROC_jeffrey} and Figure~\ref{fig:ROC_lognormal} shows ROC curves with a fixed $\alpha=0.05$. The performance improves when the read depth goes up. (ROC shows that the model with priors performs better than improper prior situation especially on the small read depth). Noticed at the lowest depth (22) with 10.0\% mutant mixture, the sensitivity and specificity value are 1 and much better than the model with improper priors for $M_j$, which definitely demonstrates the advantage of priors.

Figure~\ref{tbl:SS} shows that the sensitivity and specificity of the RVD3 of different priors compared with the model with improper priors. Log-normal prior shows a higher sensitivity and specificity value than the Jeffreys prior.
Figure~\ref{tbl:FDR} shows the false discovery rate of the RVD3 with different priors. Jeffreys prior shows a smaller false discovery rate and higher accuracy than others. It is obvious no matter Jeffreys or log-normal, the variant detection performance acquires lower FDR than the model with improper priors. Based on the various advantages for Jeffreys and log-normal prior, RVD3 can afford a more appropriate choice for the precision parameter. Here we chose Jeffreys prior model because it's a non-information prior, and more attention should be paid to false discovery rate and accuracy for variants calling research, compared with the clinical experiment or diagnosis which cares more on true positive rate and true negative rate.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Results of Jeffreys prior on yeast data
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results of Jeffreys prior on yeast data}

We demonstrated our RVD3 model with Jeffreys prior on yeast data to identify the variants.

%%%%%%%%%%%%%%%%%%%
% Appendix B: Inference of Jeffreys prior
%%%%%%%%%%%%%%%%%%%
\section{Inference of Jeffreys prior}\label{sec:appendix_mom}
We assume there is only one replicate,

@@

\begin{equation}
[-\left(\Psi_{1}(M_{j}) - \Psi_{1}(\mu_{j} M_{j})\mu_{j}^{2} - \Psi_{1}((1-\mu_{j})M_{j}){(1-\mu_{j})^{2}}\right)]^{\frac{1}{2}}
\end{equation}

%%%%%%%%%%%%%%%%%%%
% Appendix C: Key parameters for RVD3 model with log-normal prior
%%%%%%%%%%%%%%%%%%%
\section{Key parameters for RVD3 model with log-normal prior}\label{sec:appendix_mom}
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=120mm]{figs/M_lognormal.pdf}
\caption{Key parameters for RVD3 model with log-normal prior for synthetic DNA data sets.}
\label{fig:M_lognormal}
\end{center}
\end{figure}
